---
title: "Load Data"
author: "Guillem Valls, Sergio Mazzariol"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: '3'
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bank client data

## Description 

*Input variables:*

  1. age (numeric)
  2. job : type of job (categorical: 'admin.','blue-collar','entrepreneur','housemaid','management','retired','self-employed','services','student','technician','unemployed','unknown')
  3. marital : marital status (categorical: 'divorced','married','single','unknown'; note: 'divorced' means divorced or widowed)
  4. education (categorical:'basic.4y','basic.6y','basic.9y','high.school','illiterate','professional.course','university.degree','unknown')
  5. default: has credit in default? (categorical: 'no','yes','unknown')
  6. housing: has housing loan? (categorical: 'no','yes','unknown')
  7. loan: has personal loan? (categorical: 'no','yes','unknown')# related with the last contact of the current campaign:
  8. contact: contact communication type (categorical:'cellular','telephone')
  9. month: last contact month of year (categorical: 'jan', 'feb', 'mar',..., 'nov', 'dec')
  10. day_of_week: last contact day of the week (categorical:'mon','tue','wed','thu','fri')
  11. duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if duration=0 then y='no'). Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input should only be included for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.
  12. campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)
  13. pdays: number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously contacted)
  14. previous: number of contacts performed before this campaign and for this client (numeric)
  15. poutcome: outcome of the previous marketing campaign (categorical: 'failure','nonexistent','success')# social and economic context attributes
  16. emp.var.rate: employment variation rate - quarterly indicator (numeric)
  17. cons.price.idx: consumer price index - monthly indicator (numeric)
  18. cons.conf.idx: consumer confidence index - monthly indicator (numeric)
  19. euribor3m: euribor 3 month rate - daily indicator (numeric)
  20. nr.employed: number of employees - quarterly indicator (numeric)
  21. y - has the client subscribed a term deposit? (binary: 'yes','no')

# Loading packages

```{r, include=FALSE}
# Load Required Packages: to be increased over the course
library(car)  # Manual way, use for Boxplot()

requiredPackages <- c("car","knitr")
missingPackages <- requiredPackages[!(requiredPackages %in% installed.packages()[,"Package"])]

if(length(missingPackages)) install.packages(missingPackages)
lapply(requiredPackages, require, character.only = TRUE)

```


# Loading data


```{r}

setwd("C:/Users/Sergio/Dropbox/UPC/FIB/Analisis de datos y explotacion de la informacion (ADEI)/Proyecto/")
#dirwd<-"C:/Users/Sergio/Dropbox/UPC/FIB/Analisis de datos y explotacion de la informacion (ADEI)/Proyecto/bank-additional"

# Data file alread

df<-read.table('bank-additional-full.csv',header=TRUE,sep=";")

# Select your 5000 register sample (random sample)

set.seed(19101990)
llista<-sample(size=5000,x=1:nrow(df),replace=FALSE)
llista<-sort(llista)
#llista

df<-df[llista,]
save.image("set-datos.RData")
