---
title: "Deliverable 2"
author: "Guillem Valls, Sergio Mazzariol"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: '3'
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# Load Required Packages: to be increased over the course

requiredPackages <- c("mvoutlier","chemometrics","mice","missForest","missMDA","DMwR","pbkrtest","jomo","readxl","haven","sf","rgdal","missMDA","effects","FactoMineR","car","factoextra","RColorBrewer","ggplot2","dplyr","data.table", "ggmap","ggthemes","knitr","MVA")
missingPackages <- requiredPackages[!(requiredPackages %in% as.vector(installed.packages(lib.loc="~/R/win-library/3.5")[,"Package"]))]

if(length(missingPackages)) install.packages(missingPackages)
lapply(requiredPackages, require, character.only = TRUE)

```


```{r include=FALSE}
#setwd("C:/Users/Sergio/Dropbox/UPC/FIB/Analisis de datos y explotacion de la informacion (ADEI)/FIB-ADEI-Big-Data-Analysis")

setwd("C:/Users/usuario/Documents/ADEI/FIB-ADEI-Big-Data-Analysis")

load("data-INI2.RData")
```


####################  ENUNCIADO  ###########################
PCA analysis for your data should contain:

    Eigenvalues and dominant axes analysis. How many axes we have to interpret according to Kaiser and Elbow's rule?
    Individuals point of view: Are they any individuals "too contributive"? To better understand the axes meaning use the extreme individuals. Detection of multivariant outliers and influent data.
    Interpreting the axes:  Variables point of view coordinates, quality of representation, contribution of the variables  
    Perform a PCA taking into account also supplementary variables the supplementary variables can be quantitative and/or categorical  

####################  FIN ENUNCIADO  #######################
#Análisis PCA
```{r}


```


####################  ENUNCIADO  ###########################
K-Means Classification

    Description of clusters

Hierarchical Clustering

    Description of clusters

CA analysis for your data should contain your factor version of the numeric target (previous) in K= 7 (maximum 10) levels and 2 factors:

    Eigenvalues and dominant axes analysis. How many axes we have to consider
    Are there any row categories that can be combined/avoided to explain Duration target.

 MCA analysis for your data should contain:

    Eigenvalues and dominant axes analysis. How many axes we have to consider for next Hierarchical Classification stage?
    Individuals point of view: Are they any individuals "too contributive"? Are there any groups?
    Interpreting map of categories: average profile versus extreme profiles (rare categories)
    Interpreting the axes association to factor map.
    Perform a MCA taking into account also supplementary variables (use all numeric variables) quantitative and/or categorical. How supplementary variables enhance the axis interpretation?

 Hierarchical Clustering (from MCA)

    Description of clusters
    Parangons and class-specific individuals.
    Comparison of clusters obtained after K-Means (based on PCA) and/or Hierarchical Clustering (based on PCA) focusing on Duration target.
    Comparison of clusters obtained after K-Means (based on PCA) and/or Hierarchical Clustering (based on PCA) focusing on the binary target.
####################  FIN ENUNCIADO  #######################